### 2021-04-08 input/figadd.tex
figures
on examples

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with scoped flooding.}
  \end{center}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process~$a$ and Process~$d$
      become sources.  $w_{ab} = 2$; $w_{bc} = w_{bd} = 1$; $w_{cd} =
      3$.]  {\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt} \subfloat[Part C][\label{fig:addC}Process~$b$ and
      Process~$c$ receive, deliver, and forward $\alpha_{d}^{1}$ and
      $\alpha_d^3$ respectively.]{\input{input/figaddC.tex}}
    \hspace{5pt} \subfloat[Part D][\label{fig:addD}$a$ and
      $b$ discarded their received messages. $c$ still improved with $\alpha_d^2$.]
    {\input{input/figaddD.tex}}
    \caption{\label{fig:add}Efficient consistent partitioning using
      \NAMEB. Partition~$P_a$ includes $a$ while Partition~$P_d$
      includes $b$, $c$, and $d$. Process~$c$ and Process~$d$ never
      acknowledge the existence of Source~$a$, for Process~$b$ stops
      the propagation of the latter's notifications.}
  \end{center}
\end{figure*}

### 2021-04-08 input/proposal.tex
on examples

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item processes only add new partitions to the system,
\item and processes never join nor crash nor leave the system.
\end{inparaenum}
 Figure~\ref{fig:add} illustrates its behavior on a system comprising
 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and $c$
 concurrently create a partition by S-broadcasting their respective
 \underline{a}dd message: $\alpha_a^0$ and $\alpha_c^0$. They
 initialize their own state with the lowest possible bound $0$ (see
 Line~\ref{line:lowestbound}), and send a message to each of their
 neighbors by accumulating the corresponding edge weight (see
 Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
 receives $\alpha_{c}^{1}$. Since it improves its own partition
 distance, it keeps it and forwards it to its neighbors. Process $b$
 discards $\alpha_{b}^{1.5}$, for it does not improve its partition
 distance. Processes $c$ and $d$ will never hear of Process $a$'s
 partition.  In Figure~\ref{fig:addD}, processes discard last
 transiting messages. The system converged to the consistent
 partitioning. However, since processes operate using local knowledge
 only, generated traffic may be sub-optimal, for processes may
 receive, deliver, and forward messages emanating from a same source
 simply because it did not come from the shortest path yet.

@@

Unfortunately, stale control information about deleted partitions may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
\TODO{Figure showing inconsistency.}
The correctness of the partitioning depends on receipt orders at each
processes.

>>>>

Algorithm~\ref{algo:add} shows the instructions that implement such
consistent partitioning when
\begin{inparaenum}[(i)]
\item weights are scalar values,
\item processes only add new partitions to the system,
\item and processes never join nor crash nor leave the system.
\end{inparaenum}
Figure~\ref{fig:add} illustrates its behavior on a system comprising 4
processes $a$, $b$, $c$, and $d$. Process~$a$ and Process~$d$ become
the sources of their partition. They \NAMEB a notification
\underline{a}dd message: $\alpha_a^0$ and $\alpha_d^0$. They
initialize their own state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process~$b$
receives $\alpha_{d}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. In
Figure~\ref{fig:addD}, Process~$b$ discards $\alpha_{a}^{2}$, for it
does not improve its partition distance. Processes $c$ and $d$ will
never hear of Source~$a$. Ultimately, processes discard last
transiting messages. The system reached consistent partitioning.

%% However, since processes operate using local knowledge only, generated
%% traffic may be sub-optimal, for processes may receive, deliver, and
%% forward messages emanating from a same source simply because it did
%% not come from the shortest path yet.

@@

Unfortunately, stale control information about deleted partitions may
impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about other deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issue with
dynamic partitions. Both Process~$a$ and Process~$d$ add then delete
their partition concurrently. Assuming \TODO{FIFO communication
  links}, Process~$c$ receives, delivers, and forwards $\alpha_d^3$
followed by $\delta_d$. In the meantime, Process~$b$ receives,
delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
both Process~$c$ and Process~$d$ deliver the message about Partition
$P_a$, for they did not have any known partition at receipt time. On
the contrary, Process~$b$ delivers $\alpha_d^1$, for it improves its
distance to a known source. Process~$b$ then blocks Process~$a$'s
removal notification $\delta_a$. It never reaches Process~$c$ nor
Process~$d$. Also, Process~$c$ and Process~$d$ do not deliver any
$\alpha_d$ or $\delta_d$ since they already delivered it. The system
converges to an unconsistent state where some processes assume they
belong to a partition while it does not exist any longer.

Dynamic consistent partitioning depends on receipt orders at each
processes. \TODO{Transition.}
